\documentclass[11pt,a4paper]{moderncv}              % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')
\moderncvstyle{banking}                             % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue}                                % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
\nopagenumbers{}                                    % uncomment to suppress automatic page numbering for CVs longer than one page
\usepackage[utf8]{inputenc}                         % if you are not using xelatex ou lualatex, replace by the encoding you are using
\usepackage[scale=0.75]{geometry}                   % adjust the page margins    
\usepackage{import}

%----------------------------------------------------------------------------------
% personal data
%----------------------------------------------------------------------------------
\name{Eduardo}{Gobetti}
\address{Toledo, Brazil}{}{}                        % optional, remove / comment the line if not wanted; the "postcode city" and and "country" arguments can be omitted or provided empty
\phone[mobile]{+55 45 99121 0900}                   % optional, remove / comment the line if not wanted
\email{eduardo.gobetti@gmail.com}                   % optional, remove / comment the line if not wanted
% \extrainfo{additional information}                % optional, remove / comment the line if not wanted

%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
\makecvtitle

\small
{
    I graduated in TADS (Technology and Analysis in System Development) from Univel in 2008 and since then I have been working in the area of equipment, 
    server, and network maintenance, as well as user support. This role gave me access to Delphi system development. 
    In 2008, I took on the role of programmer and worked on ERP system development for poultry and swine refrigerators, as well as for the agribusiness area.\\

    From the beginning of my career, I have a affinity for the Linux operating system, which allowed me to learn more about datacenters. 
    In 2016, I had the opportunity to take on the DevOps role, where I led the implementation and automation of the pipeline, 
    as well as developed tools and scripts that are still used by the company. Since August 2019, I also lead the infrastructure team at Ecocentauro, 
    responsible for the physical restructuring of the new administrative headquarters, datacenter maintenance, internal network, and cloud.\\

    During the pandemic, I was responsible for the structure that allowed for the continuation of work from home for all employees, 
    without compromising the work scheme. Over the course of nearly 20 years in the profession, I have had the opportunity to work with various languages and technologies, 
    including Python, Golang, Dart, Containers, Bacula, VMWare ESXI, GitLab, AWS, and Kong.\\

    I enjoy the challenge my area provides, allowing me to improve the team's productive process, solve complex problems, 
    and anticipate possible situations that may affect the smooth operation of the company's work.
}

\vspace{6pt}
\section{Professional experience}

\vspace{6pt}
\begin{itemize}

\item
{\cventry{2021--2023}
{}
{SRE | Cloud and DevOps Engineer}
{Americanas}
{}
{
I worked on orchestration of containers with ECS (Fargate or EC2) and Kubernetes EKS (with EC2), I created scalable and resilient environments.
My expertise spans major AWS services while managing ElasticSearch and Apache Kafka clusters for optimization and availability.    
I also have experience in advanced monitoring, ensuring essential metrics and high quality of services.}
}

\vspace{6pt}
\item
{\cventry{2019--2021}
{}
{Tech lead}
{Ecocentauro}
{}
{
I led a highly skilled infrastructure and DevOps/SysAdmin team in a cloud-based environment. 
My role involved guiding and collaborating with the team to execute complex projects effectively and maintain critical systems optimally. 
I managed infrastructure building, scalability, and security, ensuring efficient operations in a constantly evolving environment.}
}

\vspace{6pt}
\item
{\cventry{2016--2019}
{}
{Devops}
{Ecocentauro}
{}
{Developed and implemented automated processes, creating pipelines for a variety of applications in languages.}
}

\newpage

\vspace{6pt}
\item
{\cventry{2012--2016}
{}
{Delphi developer}
{Ecocentauro}
{}
{As a FullStack Developer, I played a key role in the development of an ERP system, directly contributing to its restructuring and architectural improvement.}
}

\vspace{6pt}
\item
{\cventry{2008--2012}
{}
{Delphi developer}
{Diplomata S/A Industrial}
{}
{Conducted analyzes and developed solutions for corrections and improvements in the ERP system}
}

\vspace{6pt}
\item
{\cventry{2005--2008}
{}
{Helpdesk}
{Diplomata S/A Industrial}
{}
{Hardware Support. Task automation script. Server monitoring and management}
}

\end{itemize}

\vspace{6pt}
\section{Education}
\vspace{5pt}

\subsection{Academic Qualifications}

\vspace{5pt}

\begin{itemize}
\item{\cventry{2005--2008}
{Technology in systems analysis and development}
{Univel}
{Cascavel}
{Bachelor's Degree}
{}
}
\end{itemize}

\vspace{6pt}
\section{Languages}
\cvitemwithcomment{English}{Advanced}{}
\cvitemwithcomment{Italian}{Basic}{}


\section{skils}
\cvlistdoubleitem{Gitlab}{Python}
\cvlistdoubleitem{Jenkins}{PostgreSQL}
\cvlistdoubleitem{Prometheus}{Delphi}
\cvlistdoubleitem{Docker}{IBM Db2}
\cvlistdoubleitem{Kubernetes}{Go}
\cvlistdoubleitem{Datadog}{Jira}
\cvlistdoubleitem{Linux}{Aws}
\cvlistdoubleitem{Apache Kafka}{Elastic Stack (ELK)}
\end{document}